---
title: "BSMM-lab-2"
subtitle: "BSMM 8740 Fall 2023"
author: "Rajasree Bammidi"
date: "2023-09-27"
format: html
editor: visual
self-contained: true
---

## Setup

Load packages and data:

```{r load-pkg-data}
#| message: false
install.packages("tidyverse")
install.packages("gt")           # for making display tables
install.packages("gtExtras")     # helper functions for beautiful tables
install.packages("DataExplorer")
install.packages("tidymodels")
install.packages("gt")
library(magrittr)     # the pipe
library(tidyverse)    # for data wrangling + visualization
```

```{r}
library(tidymodels)   # for modeling
library(gt)           # for making display tables
library(gtExtras)     # helper functions for beautiful tables
library(DataExplorer) #
the_tate <- readr::read_delim("data/the-tate-collection.csv", ";", escape_double = FALSE, trim_ws = TRUE)
the_tate_artists <- readr::read_csv("data/the-tate-artists.csv")
```

## Exercises

### Exercise 1

```{r}
glimpse(the_tate_artists)
```

```{r}
View(the_tate)
View(the_tate_artists)
```

```{r}
glimpse(the_tate)
```

```{r}
summary(the_tate)
```

```{r}
#summarize function use to find summary of each artist
the_tate %>% dplyr::group_by(the_tate$artist) %>% 
dplyr::summarize(N=n(),min_yearworking= min(the_tate$year,na.rm = TRUE),
max_yearworking= max(the_tate$year,na.rm = TRUE),
min_aquistionyear=min(the_tate$acquisitionYear, na.rm = TRUE),
max_acquisitionyear=max(the_tate$year,na.rm = TRUE)  )
```

```{r}
# Load the required library
library(dplyr)
# Calculate the number of unique artists using select
unique_artists_count <- the_tate %>%
  select(artist) %>%
  distinct() %>%
  nrow()
unique_artists_count
```

```{r}
# Find the range of years artists worked
min_year_worked <- min(the_tate$year,na.rm = TRUE)
max_year_worked <- max(the_tate$year,na.rm = TRUE)

# Find the range of acquisition years
min_acquisition_year <- min(the_tate$acquisitionYear, na.rm = TRUE)
max_acquisition_year <- max(the_tate$acquisitionYear, na.rm = TRUE)


cat("The the_tate dataset has", unique_artists_count, "unique artists who worked from",
    min_year_worked, "to", max_year_worked, ".\n")

cat("The works were acquired between the years", min_acquisition_year, "and", max_acquisition_year, ".\n")
```

```{r}
DataExplorer::introduce(the_tate)
```

```{r}
DataExplorer::introduce(the_tate_artists)
```

```{r}
DataExplorer::plot_missing(the_tate)
```

```{r}
DataExplorer::plot_missing(the_tate_artists)
```

```         
The the_tate dataset has 3336 unique artists who worked from 1545 to 2012 . The works were acquired between the years 1823 and 2013 .
```

### Exercise 2

```{r}
works_with_missing_years <- sum(is.na(the_tate$year))
works_with_missing_years
```

How number of works with missing dates is **5397**.

```{r}
the_tate|>dplyr::filter(is.na(year))|>dplyr::distinct(artist)
```

```{r}
artists_with_missing_dates <- the_tate %>%
  filter(is.na(year)) %>%
  distinct(artist) %>%
  nrow()

artists_with_missing_dates
```

```{r}
# Count the number of works missing years for each artist
artist_missing_year_counts <- the_tate|>dplyr::filter(is.na(year)) %>% 
  group_by(artist) %>%
  summarise(missing_years = sum(is.na(year))) %>%
  arrange(desc(missing_years)) %>%
  as_tibble()

# Determine how many artists have works with missing years
artists_with_missing_years <- nrow(artist_missing_year_counts)
artists_with_missing_years

# Calculate the percent of total missing data for each artist
artist_missing_year_counts <- artist_missing_year_counts %>%
  mutate(percentage = (missing_years / works_with_missing_years) * 100)

# Calculate the cumulative percent of missing data
artist_missing_year_counts <- artist_missing_year_counts %>%
  mutate(cumulative_percentage = cumsum(percentage))

# Identify the smallest number of artists needed to resolve at least 50% of the missing year data
artists_to_resolve_50_percent <- min(which(artist_missing_year_counts$cumulative_percentage >= 50))

artists_to_resolve_50_percent
```

The number of artists whose works have missing dates is **461**.

It would require resolving missing year data for only **11** artists resolve resolve at least 50% of the missing data.

The missing year data likely to be classified as **MAR**.

### Exercise 3

The artist with the most works in the Tate collection is \_\_\_.

The artist with the tenth-most works in the Tate collection is \_\_\_.

### Exercise 4

The artist with the greatest number of works in the Tate collection represent \_\_\_% of the total number of works

### Exercise 5

There are \_\_ duplicate artist-title pairs

### Exercise 6

The artist with the largest work in the tate collection is \_\_\_

The artist with the smallest work in the collection is \_\_\_. The smallest work has area \_\_\_ $\text{cm}^2$

### Exercise 7

...

### Exercise 8

The annual return in the SPX price in 2020 was \_\_\_%.

The corresponding price volatility was \_\_\_%.

### Exercise 9

The period volatility was \_\_\_.\_%

### 
